A Hierarchical Bayesian Framework for Stellar Obliquity Distribution Inference

### 2023-02-10 src/tex/ms.tex
[showyourwork] overleaf sync

\section{Reproducibility}\label{sec:reproducibility}
This study was carried out using the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork} \citep{Luger2021}, which leverages continuous integration to programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript. 
Each figure caption contains one link to the script used to make the figure (at the commit corresponding to the current build of the manuscript).
The git repository associated with this study is publicly available at \url{https://github.com/jiayindong/obliquity}.
A Jupyter notebook with examples of the stellar obliquity distribution inference can be found in the same repository.

>>>>

\section{Reproducibility}\label{sec:showyourwork}
This study was carried out using the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork} \citep{Luger2021}, which leverages continuous integration to programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript. 
Each figure caption contains one link to the script used to make the figure (at the commit corresponding to the current build of the manuscript).
The git repository associated with this study is publicly available at \url{https://github.com/jiayindong/obliquity}.
A Jupyter notebook with examples of the stellar obliquity distribution inference can be found in the same repository.
